ShrinkNets

### 2018-01-05 paper/paper.tex
Some typos

This choice come from the Lasso loss [ref] and we use it for the same reason:
it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
are set to zer, and since zeros entries in $\theta$ correspond to dead neurons,
lambda effectively control the number of neurons/channels in the entire
network.
Next, we explain how to implement ShrinkNets efficiently.

\textbf{Software architecture\footnote{The code is available as Python/PyTorch library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename the repository ?}} :}\textit{Filter Vectors} can easily be implemented in a few lines of code
in many existing deep learning frameworks. However, in ShrinkNets we assume
that we start with obviously oversized networks. If disabled neurons are not
quickly removed, the overhead might caused the training process to be
significantly slower than classic neural networks. This is why we want to
support what we call garbage collection: removing the weights in the layers
that are responsible(or using) features that are disabled.
\par To be able to catpure this relationship between layers we agumented
\textit{Pytorch} (the framework we used as the foundation of our implementation)
with a graph structure very similar to the one available in Keras [ref].
In this graph edges are effectively event hubs responsible for propagating
\textit{feature removal} events to subscribing layers. ShrinkNet layers are
agumented to emit and react to these events but also propagate the event
further if has an impact at the other endpoint of the layer (input or output).
\par This event-based implementation coordinated by edges makes it very easy
to integrate new layers in the library. We even provide automatic wrapping
for layers from pytorch if they have no internal state. For more complex ones,
we provide utilitaries that makes the implementation very concise.

@@

One of our main goal is to help finding neural network architectures that
perform reasonably well faster than existing techniques. For simplicity,
we will try to see how ShrinkNets perform when doing random search. However,
we believe that the results generalize to more complex methods, most of them
might actually benefit a lot from the reduction in the dimensionality of the
hyper-parameter space.

\par To isolate the effect of ShrinkNets we will consider very simple architectures
We will be using multi-layer perceptrons (with three hidden layers) and
convolutional neural networks (With the LeNet-5 architecture). For this experiment
we will assume we have no information about the size except an upper bound of
$50$ channels per convolutional layer and $5000$ neuron for fully connected layers.
We try to find the appropriate size of the network using classical neural networks
and ShrinkNets. To make sure that we are as fair as possible and since one might
argue that ShrinkNets is also regularizing the network in addition to finding the
size, we will also considered regualrized classic networks using the most commonly
used technique the $L_2$ penalty [ref].
\par The experiment consist in sampling parameters randomly for each class of
network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation accuracy and evaluate it
on the testing set. We repeat the process for 50 models. This evaluation was done
on \texttt{MNIST} [ref], \texttt{FashionMNIST} [ref] and \texttt{CIFAR10} [ref]. The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.

We can see that the distributions for ShrinkNets are consistently better than the
others for all datasets and both architectures. It shows that by training fewer
networks, we are likely to obtain on-par or even better models which effectively
reduces the cost of hyper-parameter optimization. In some cases the best ShrinkNets
models outperforms the best model of the other techniques.

@@

\par There are many methods in the litterature that try to simplify the neural
network. Most of them focuses on removing connections (eg: [ref], [ref]).
However, most hardware (GPU's, TPUS, TensorCores) do not really leverage sparsity
in the connections efficiently. On the other side, ShrinkNets and some others [ref]
and [ref] try to remove entire neuron instead of connections. This is very
usefull because it reduce the size of the matrices, producing speed-up on
every device. ShrinkNets improves on [ref] because it removes neurons during
training, speeding up the rest of the process and beats [ref] on convergence
speed and because it does not need to change the optimizer. To the best of our
knowledge this is also the first contribution that tries to learn the number of
channels of a convolutional neural network.

>>>>

This choice come from the Lasso loss [ref] and we use it for the same reason:
it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
are set to zer0, and since zero entries in $\theta$ correspond to dead neurons,
lambda effectively control the number of neurons/channels in the entire
network.
Next, we explain how to implement ShrinkNets efficiently.

\textbf{Software architecture\footnote{The code is available as Python/PyTorch
    library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
      the repository ?}}: }\textit{Filter Vectors} can easily be implemented in
a few lines of code in many existing deep learning frameworks. However, in
ShrinkNets, we assume that we start with obviously oversized networks. If
disabled neurons are not quickly removed, the overhead might cause the training
process to be significantly slower than classic neural networks. This is why we
want to support what we call garbage collection: removing the weights in the
layers that are responsible (or using) features that are disabled.  \par To be
able to catpure this relationship between layers, we agumented \textit{Pytorch}
(the framework we used as the foundation of our implementation) with a graph
structure very similar to the one available in Keras [ref].  In this graph,
edges are effectively event hubs responsible for propagating \textit{feature
  removal} events to its endpoints. ShrinkNet layers are designed to emit and
react to these events but also propagate the event further if has an impact at
the other endpoint of the layer (input or output) \gl{What I mean here is: if
  the event comes from the output, it might be propagated to the inputs, and
  the other way around}.  \par This event-based implementation coordinated by
edges makes it very easy to integrate new layers in the library. We even
provide automatic wrapping for layers from \textit{PyTorch} if they have no
internal state. For more complex ones, we provide utilitaries that makes the
implementation very concise.

@@

One of our main goal is to help finding neural network architectures that
perform reasonably well faster than existing techniques. For simplicity, we
will try to see how ShrinkNets perform when doing random search over a sub set
of the hyper-parameter space (we will fix everything except the size-related
parameters). However, we believe that the results generalize to more complex
methods, most of them might actually benefit a lot from the reduction of the
dimensionality of the hyper-parameter space.

\par To isolate the effect of ShrinkNets we will consider two very simple
architectures: multi-layer perceptrons (with three hidden layers) and the
\textit{LeNet-5} model. For this experiment we assume we have no prior
information about the size except an upper bound of $50$ channels per
convolutional layer and $5000$ neuron for fully connected layers.  We try to
find the appropriate size of the network using classical neural networks and
ShrinkNets. To make sure that we are as fair as possible and since one might
argue that ShrinkNets is also regularizing the network in addition to finding
the size, we will also considered regularized classic networks using the most
commonly used technique: the $L_2$ penalty [ref].
\par The experiment consist in sampling parameters randomly for each class of
network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation set and evaluate it
on the testing set. We repeat the process for 50 models. This evaluation was done
on \texttt{MNIST} [ref], \texttt{FashionMNIST} [ref] and \texttt{CIFAR10} [ref]. The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.

We can see that the distributions for ShrinkNets are consistently better than the
others for all datasets and both architectures. It shows that by training fewer
networks, we are likely to obtain on-par or even better models which effectively
reduces the cost of hyper-parameter optimization. In some cases the best ShrinkNets
models even outperforms the best model of the other techniques.

@@

\par There are many methods in the litterature that try to simplify the neural
network structure. Most of them focuses on removing connections (eg: [ref],
[ref]).  However, most hardware (GPU's, TPUS, TensorCores) do not really
leverage sparsity in the connections efficiently. On the other side, ShrinkNets
and some others [ref] and [ref] try to remove entire neuron instead of
connections. This is very usefull because it reduces the size of the matrices,
producing speed-up on every device. ShrinkNets improves on [ref] because it
removes neurons during training, speeding up the rest of the process and beats
[ref] on convergence speed and because it does not need to change the
optimizer. To the best of our knowledge this is also the first contribution
that tries to learn the number of channels of a convolutional neural network.
